\sf Retraction-based first-order feasible methods for difference-of-convex programs with smooth inequality and simple geometric constraints

### 2022-04-24 response_to_referee_v1.tex

	\textbf{Response:} Thanks for the comment. In fact,
\begin{equation*}
\begin{aligned}
\sigma^2 &= \|A(\widehat x_{\rm spgl1} + \tau(A^\dagger b - \widehat x_{\rm spgl1})) - b\|^2\\
 &=\tau^2\|A(A^\dagger b - \widehat x_{\rm spgl1})\|^2 + 2\tau\|A(A^\dagger b - \widehat x_{\rm spgl1})\|\|A(\widehat x_{\rm spgl1} - b\| + \|A(\widehat x_{\rm spgl1} - b\|^2
\end{aligned}
\end{equation*}
which is a quadratic function in $\tau$. One can then obtain a closed form formula for $\tau$.

	\item  \textit{\textbf{Reviewer:}} \textit{Numerical results: As far as I see, Algorithm 3 does not require to find a completely feasible initial point ($x_0\in F$) but just in C ($x_0\in C$). I did not find any statement about how the initial point is chosen for ESQM$_{\rm ls}$. In principle, SPGL1 and Slater point are not needed. Therefore, it is not fair to say that FPA is faster since the sum of the iteration time plus the required initialization exceeds the CPU time of ESQM$_{\rm ls}$. Would it be any other cheaper way to compute $x_0$?}

	\textbf{Response:} Thanks for the comment. Following your comment, we explore the effect of the choice of initial points for the two algorithms in solving (6.2).

Table 1 below shows the computational results when the initial points for the ESQMs are chosen as
$x^0 = (0, 0, \cdots, 0)$ and the initial points for the FPA$_{\rm retract}$ is chosen as (6.6). From Table 1, one can see that 
the recovery errors of FPA$_{\rm retract}$ and ESQM$_{\rm ls}$ are comparable, and the sum time of generated a Slter Point, SPGL1 and FPA$_{\rm retract}$ is comparable to the time of ESQM$_{\rm ls}$.

%Although ESQM$_{\rm ls}$ becomes faster when the initial point is zero, FPA$_{\rm retract}$ with initial point chosen in (6.6) still seems to be faster than ESQM$_{\rm ls}$ with zero initial point.

%{\color{red} TK: Why is FPA also using zero initial point? That does not make any sense. Don't we need feasible starting points?

% We only need ONE table, I think: ESQM with zero initial point and our method with our suggested initial point. Please re-do the table.}

\begin{table}[H]
\caption{Computational results for problem (6.2) with initial point $x^0 = (0, 0, \cdots, 0)$ for ESQM 
and the initial points for the FPA$_{\rm retract}$ is chosen as (6.6).}\label{table1}
\begin{center}
{\footnotesize
\begin{tabular}{|c|c|c|c|c|c|c|}\hline
\phantom{\diagbox{Date}{$i$}} & \multicolumn{1}{|c|}{Method} & \multicolumn{1}{|c|}{$i = 2$} & \multicolumn{1}{c|}{ $i = 4$ } & \multicolumn{1}{c|}{ $i = 6$ } & \multicolumn{1}{|c|}{ $i = 8$ } & \multicolumn{1}{c|}{ $i = 10$ }\\\cline{1-7}
\multirow{7}*{CPU time} & \multirow{1}*{QR}
&   0.52 &   3.13 &   9.30 &  22.65 &  44.45\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{Slater}
&   0.01 &   0.03 &   0.05 &   0.09 &   0.15\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{SPGL1}
&   1.54 &   6.84 &  16.39 &  30.45 &  42.97\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
&   3.01 &  13.54 &  29.17 &  53.66 & 105.66\\\cline{2-7} \multirow{1}*{}  & \multirow{1}*{Slater + SPGL1 + FPA$_{\rm retract}$}
&   4.57 &  20.40 &  45.60 &  84.20 & 148.78\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
&   5.13 &  24.23 &  56.41 & 105.38 & 173.96\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
&   4.61 &  20.76 &  47.71 &  88.30 & 145.13\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
&  13.91 &  59.10 & 134.39 & 241.26 & 386.69\\\cline{1-7} \multirow{4}*{Iter} & \multirow{1}*{FPA$_{\rm retract}$}
&    342 &    406 &    398 &    418 &    533\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
&    766 &    970 &   1027 &   1104 &   1175\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
&    776 &    873 &    905 &    952 &   1002\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
&   2446 &   2559 &   2593 &   2626 &   2682\\\cline{1-7} \multirow{5}*{RecErr} & \multirow{1}*{SPGL1}
&  0.054 &  0.055 &  0.048 &  0.046 &  0.066\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
&  0.030 &  0.033 &  0.033 &  0.035 &  0.036\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
&  0.030 &  0.033 &  0.033 &  0.035 &  0.036\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
&  0.030 &  0.033 &  0.033 &  0.035 &  0.036\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
&  0.030 &  0.033 &  0.033 &  0.035 &  0.036\\\cline{1-7} \multirow{5}*{Residual} & \multirow{1}*{SPGL1}
& -2.01e-04 & -1.63e-04 & -1.87e-04 & -1.40e-04 & -9.35e-05\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
& 5.89e-16 & 1.40e-15 & 5.99e-16 & 2.73e-15 & 1.05e-16\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
& 1.32e-10 & 1.10e-10 & 1.14e-10 & 1.13e-10 & 1.09e-10\\\cline{2-2} \multirow{1}*{}      & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
& 1.08e-10 & 9.93e-11 & 1.02e-10 & 9.59e-11 & 9.54e-11\\\cline{2-2} \multirow{1}*{}      & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
& 1.01e-10 & 9.83e-11 & 9.26e-11 & 9.35e-11 & 9.32e-11\\\cline{1-7}
\end{tabular}
}
\end{center}
\end{table}
%\caption{Computational results for problem (6.2) with initial point $x^0 = (0, 0, \cdots, 0)$ for ESQM}\label{table1}
%\phantom{\diagbox{Date}{$i$}} & \multicolumn{1}{|c|}{Method} & \multicolumn{1}{|c|}{$i = 2$} & \multicolumn{1}{c|}{ $i = 4$ } & \multicolumn{1}{c|}{ $i = 6$ } & \multicolumn{1}{|c|}{ $i = 8$ } & \multicolumn{1}{c|}{ $i = 10$ }\\\cline{1-7}
%&   0.50 &   3.11 &   9.79 &  22.95 &  43.99\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{Slater}
%&   0.01 &   0.02 &   0.05 &   0.09 &   0.15\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{SPGL1}
%&   1.38 &   7.54 &  15.69 &  28.50 &  50.25\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
%&  14.09 &  62.33 & 139.27 & 241.40 & 388.70\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
%&   4.92 &  25.75 &  59.09 & 102.56 & 170.23\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
%&   4.42 &  21.80 &  49.89 &  86.37 & 142.02\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
%&  13.36 &  59.88 & 135.25 & 236.76 & 378.49\\\cline{1-7} \multirow{4}*{Iter} & \multirow{1}*{FPA$_{\rm retract}$}
%&   1638 &   1847 &   1885 &   1883 &   1957\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
%&    759 &   1025 &   1075 &   1080 &   1158\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
%&    767 &    913 &    946 &    941 &    991\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
%&   2439 &   2579 &   2618 &   2620 &   2670\\\cline{1-7} \multirow{5}*{RecErr} & \multirow{1}*{SPGL1}
%&  0.060 &  0.051 &  0.055 &  0.055 &  0.046\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
%&  0.030 &  0.034 &  0.035 &  0.034 &  0.036\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
%&  0.030 &  0.034 &  0.035 &  0.034 &  0.036\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
%&  0.030 &  0.034 &  0.035 &  0.034 &  0.036\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
%&  0.030 &  0.034 &  0.035 &  0.034 &  0.036\\\cline{1-7} \multirow{5}*{Residual} & \multirow{1}*{SPGL1}
%& -1.72e-04 & -2.10e-04 & -1.53e-04 & -1.37e-04 & -1.26e-04\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
%& 1.69e-15 & 1.35e-15 & 2.79e-16 & -7.54e-16 & -1.42e-15\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
%& 1.21e-10 & 1.22e-10 & 1.12e-10 & 1.10e-10 & 1.11e-10\\\cline{2-2} \multirow{1}*{}      & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
%& 1.06e-10 & 9.98e-11 & 9.32e-11 & 9.36e-11 & 9.10e-11\\\cline{2-2} \multirow{1}*{}      & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
%& 1.01e-10 & 9.93e-11 & 9.77e-11 & 9.47e-11 & 9.60e-11\\\cline{1-7}
%\caption{Computational results for problem (6.2) with initial point $x^0$ is given as in (6.6) for all algorithms}\label{table1}
%&   0.47 &   3.05 &   9.83 &  23.25 &  44.84\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{Slater}
%&   0.01 &   0.02 &   0.05 &   0.09 &   0.15\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{SPGL1}
%&   1.59 &   7.35 &  15.20 &  30.17 &  48.54\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
%&   3.40 &  12.30 &  37.94 &  56.91 &  97.89\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
%&   5.43 &  23.38 &  61.11 & 104.34 & 173.99\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
%&   4.64 &  20.41 &  51.46 &  88.36 & 146.46\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
%&  13.25 &  58.83 & 136.92 & 239.48 & 382.51\\\cline{1-7} \multirow{4}*{Iter} & \multirow{1}*{FPA$_{\rm retract}$}
%&    420 &    368 &    520 &    444 &    493\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
%&    893 &    937 &   1113 &   1099 &   1186\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
%&    839 &    863 &    977 &    963 &   1025\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
%&   2508 &   2550 &   2653 &   2650 &   2702\\\cline{1-7} \multirow{5}*{RecErr} & \multirow{1}*{SPGL1}
%&  0.061 &  0.045 &  0.066 &  0.051 &  0.054\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
%&  0.032 &  0.032 &  0.035 &  0.035 &  0.037\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
%&  0.032 &  0.032 &  0.035 &  0.035 &  0.037\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
%&  0.032 &  0.032 &  0.035 &  0.035 &  0.037\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
%&  0.032 &  0.032 &  0.035 &  0.035 &  0.037\\\cline{1-7} \multirow{5}*{Residual} & \multirow{1}*{SPGL1}
%& -2.72e-04 & -2.20e-04 & -1.41e-04 & -1.19e-04 & -1.30e-04\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
%& -1.86e-16 & 2.98e-16 & 1.85e-15 & -5.27e-16 & -1.31e-15\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
%& 1.08e-10 & 1.15e-10 & 1.01e-10 & 1.09e-10 & 1.05e-10\\\cline{2-2} \multirow{1}*{}      & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
%& 9.49e-11 & 9.50e-11 & 8.90e-11 & 9.60e-11 & 9.95e-11\\\cline{2-2} \multirow{1}*{}      & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
%& 9.35e-11 & 9.91e-11 & 9.14e-11 & 9.44e-11 & 9.34e-11\\\cline{1-7}

@@

	\item  \textit{\textbf{Reviewer:}} \textit{ c) Theorem 3.2. Please recall that $u^k = \tilde u$.}

	\textbf{Response:} Thanks for the comment. We recalled that the sequence $\{u^k\}$ is generated by Algorithm 1 in the statement of the theorem. A similar modification is done in Theorem 4.2.

	\item \textit{\textbf{Reviewer:}} \textit{ d) Assumption 4.1. The notation $\xi$ has already been employed for the subgradient of $P_2$.}

    \textbf{Response:} Thanks for the comment. We replace $\varphi$ with $\phi$ in Definition 2.1 and replace $\xi$ with $\varphi$ in Assumption 4.1 and beyond.

### 2022-04-25 SQP_Retract_rev1.tex
Updated the Table 1

\begin{table}[h]
{\color{blue}
\caption{Computational results for problem \eqref{E3}}\label{table1}
\begin{center}
{\footnotesize
\begin{tabular}{|c|c|c|c|c|c|c|}\hline
\phantom{\diagbox{Date}{$i$}} & \multicolumn{1}{|c|}{Method} & \multicolumn{1}{|c|}{$i = 2$} & \multicolumn{1}{c|}{ $i = 4$ }
& \multicolumn{1}{c|}{ $i = 6$ } & \multicolumn{1}{|c|}{ $i = 8$ } & \multicolumn{1}{c|}{ $i = 10$ }\\\cline{1-7}
\multirow{7}*{CPU time} & \multirow{1}*{QR}
&   0.47 &   3.05 &   9.83 &  23.25 &  44.84\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{Slater}
&   0.01 &   0.02 &   0.05 &   0.09 &   0.15\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{SPGL1}
&   1.59 &   7.35 &  15.20 &  30.17 &  48.54\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
&   3.40 &  12.30 &  37.94 &  56.91 &  97.89\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
&   5.43 &  23.38 &  61.11 & 104.34 & 173.99\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
&   4.64 &  20.41 &  51.46 &  88.36 & 146.46\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
&  13.25 &  58.83 & 136.92 & 239.48 & 382.51\\\cline{1-7} \multirow{4}*{Iter} & \multirow{1}*{FPA$_{\rm retract}$}
&    420 &    368 &    520 &    444 &    493\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
&    893 &    937 &   1113 &   1099 &   1186\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
&    839 &    863 &    977 &    963 &   1025\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
&   2508 &   2550 &   2653 &   2650 &   2702\\\cline{1-7} \multirow{5}*{RecErr} & \multirow{1}*{SPGL1}
&  0.061 &  0.045 &  0.066 &  0.051 &  0.054\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
&  0.032 &  0.032 &  0.035 &  0.035 &  0.037\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
&  0.032 &  0.032 &  0.035 &  0.035 &  0.037\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
&  0.032 &  0.032 &  0.035 &  0.035 &  0.037\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
&  0.032 &  0.032 &  0.035 &  0.035 &  0.037\\\cline{1-7} \multirow{5}*{Residual} & \multirow{1}*{SPGL1}
& -2.72e-04 & -2.20e-04 & -1.41e-04 & -1.19e-04 & -1.30e-04\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
& -1.86e-16 & 2.98e-16 & 1.85e-15 & -5.27e-16 & -1.31e-15\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
& 1.08e-10 & 1.15e-10 & 1.01e-10 & 1.09e-10 & 1.05e-10\\\cline{2-2} \multirow{1}*{}      & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
& 9.49e-11 & 9.50e-11 & 8.90e-11 & 9.60e-11 & 9.95e-11\\\cline{2-2} \multirow{1}*{}      & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
& 9.35e-11 & 9.91e-11 & 9.14e-11 & 9.44e-11 & 9.34e-11\\\cline{1-7}
\end{tabular}
}
\end{center}
}
\end{table}

>>>>

\begin{table}[h]
{\color{blue}
\caption{Computational results for problem \eqref{E3}}\label{table1}
\begin{center}
{\footnotesize
\begin{tabular}{|c|c|c|c|c|c|c|}\hline
\phantom{\diagbox{Date}{$i$}} & \multicolumn{1}{|c|}{Method} & \multicolumn{1}{|c|}{$i = 2$} & \multicolumn{1}{c|}{ $i = 4$ }
& \multicolumn{1}{c|}{ $i = 6$ } & \multicolumn{1}{|c|}{ $i = 8$ } & \multicolumn{1}{c|}{ $i = 10$ }\\\cline{1-7}
\multirow{7}*{CPU time} & \multirow{1}*{QR}
&   0.56 &   3.34 &  10.69 &  44.45 &  49.15\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{Slater}
&   0.01 &   0.02 &   0.05 &   0.16 &   0.16\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{SPGL1}
&   1.69 &   7.41 &  16.76 &  39.55 &  42.02\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
&   3.26 &  14.59 &  30.10 &  69.41 & 104.50\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
&   5.39 &  25.64 &  56.20 & 134.31 & 169.64\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
&   4.99 &  21.87 &  48.51 & 114.55 & 142.53\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
&  14.95 &  62.79 & 136.41 & 308.62 & 377.03\\\cline{1-7} \multirow{4}*{Iter} & \multirow{1}*{FPA$_{\rm retract}$}
&    342 &    406 &    398 &    418 &    533\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
&    756 &    965 &   1002 &   1078 &   1161\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
&    773 &    870 &    905 &    952 &   1002\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
&   2446 &   2559 &   2595 &   2629 &   2684\\\cline{1-7} \multirow{5}*{RecErr} & \multirow{1}*{SPGL1}
&  0.054 &  0.055 &  0.048 &  0.046 &  0.066\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
&  0.030 &  0.033 &  0.033 &  0.035 &  0.036\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
&  0.030 &  0.033 &  0.033 &  0.035 &  0.036\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
&  0.030 &  0.033 &  0.033 &  0.035 &  0.036\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
&  0.030 &  0.033 &  0.033 &  0.035 &  0.036\\\cline{1-7} \multirow{5}*{Residual} & \multirow{1}*{SPGL1}
& -2.01e-04 & -1.63e-04 & -1.87e-04 & -1.40e-04 & -9.35e-05\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
& 5.89e-16 & 1.40e-15 & 5.99e-16 & 2.73e-15 & 1.05e-16\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
& 1.10e-10 & 1.17e-10 & 1.07e-10 & 1.01e-10 & 1.13e-10\\\cline{2-2} \multirow{1}*{}      & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
& 9.90e-11 & 8.93e-11 & 9.89e-11 & 1.00e-10 & 9.28e-11\\\cline{2-2} \multirow{1}*{}      & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
& 1.01e-10 & 9.20e-11 & 8.95e-11 & 9.14e-11 & 9.62e-11\\\cline{1-7}
\end{tabular}
}
\end{center}
}
\end{table}
